\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-12 bmc_section.tex
.

\inclfig[width=0.50\linewidth]{vdp_graph.pdf}{$\epsilon$-RTS for the
Van der Pol abstraction. Each edge corresponds to an affine map $F$
and summarizes the transition relation.}{vdp-graph}
\begin{example}
    Coming back to~\exref{vdp}, \figref{vdp-graph} %and\tabref{vdp-pwa}
    shows the abstract reachability graph with its transition
    relations. The relational maps are omitted for brevity.
    Note that self loops result when an observed trajectory
    segment begins and ends in the same cell.
    The graph $\scr{H}(0.1)$ can now be viewed as a
    transition system $\tupleof{C,\x,\scrT,C_0,\HybridStates_0}$,
    where $C \in vertices(\scr{H}(0.1))$ and $\x \in
    \HybridStates$. A transition $\tau \in \scrT$ is of the form
    $\tupleof{C, C',\rho_{\tau}}$, where $\rho_{\tau}(\x,\x')
    \subseteq \setof{R_{(C,C')}(\x,\x') |( C,C') \in
    edge(\scr{H}(0.1))}$.

\mypara{\emph{Check Counter-example}}: The infinite state (but finite location) transition system can
    be model checked to find a concrete counter-example, which if
    exists, can indicate the existence of a similar trace in the
    original black-box system $\System$. The latter check is carried
    out as before, using the numerical simulation function
        $\simulate$~\footnote{For the given example, the model checker is unable to
        find a counter-example.}.
\end{example}

>>>>

\inclfig[width=0.50\linewidth]{vdp_graph.pdf}{$\epsilon$-RTS for the
Van der Pol abstraction. Each edge corresponds to an affine map $F$
and summarizes the transition relation.}{vdp-graph}
\begin{example}
    Coming back to~\exref{vdp}, \figref{vdp-graph}
    shows the abstract reachability graph with its transition
    relations. The relational maps are omitted for brevity.
    Note that self loops result when an observed trajectory
    segment begins and ends in the same cell. This graph can now be
    model checked for counter-examples. Note that each path in the
    graph corresponds to a conunction of affine constraints (when the
    maps are affine). A counter-example exists if any of the
    linear programs (paths) are feasible. The over all BMC problem
    involves reasoning over disjunctions due to the presence of
    multiple paths.

% \mypara{\emph{Check Counter-example}}: The infinite state (but finite location) transition system can
%     be model checked to find a concrete counter-example, which if
%     exists, can indicate the existence of a similar trace in the
%     original black-box system $\System$. The latter check is carried
%     out as before, using the numerical simulation function
%         $\simulate$~\footnote{For the given example, the model checker is unable to
%         find a counter-example.}.
\end{example}
